Not submitted on time.
%\subsubsection*{State of MathSoc Operational Accounts}
%\begin{itemize}
%	\item
%\end{itemize}

%\subsubsection*{State of Other Affairs}
%\begin{itemize}
%	\item
%\end{itemize}

%\subsubsection*{Advancement and Other Announcements}
%\begin{itemize}
%	\item
%\end{itemize}
\subsection*{Email}
Tristan,

Sorry for the late notice but I won't be able to make it to tomorrow's meeting because of group projects but I wanted to let you and Council know what the state of finances are as of now.

I think Lily may be asking for ~2k reimbursement for novelties. Since novelties is revenue neutral (we usually profit) and we are getting our student fees this Wednesday from Feds (confirmed), we should be ok in terms of cash flow and won't need assistance from mathnews.

The current budget sits at ~650 surplus, though it may be far less given lower than expected office revenue (\$1200 less than budgeted) and high cost of toner (\$600 more than budgeted). I have not yet received reimbursements for all club events but IF club spending goes according to budget, my estimate is that we're at a deficit of ~1200. It could be possible that not all clubs max out their budget but if any club is looking for more money I don't think we're in a position where we can back it unless they have very good reason.

Tldr, budgeted revenue was way higher than actuals so we're likely at a deficit unless some clubs decide not to max their budget. Lily should still be reimbursed though because we'll get the novelties revenue back eventually.

Please email me if there are any questions; I'll try to check during my group meeting, though I expect we'll be very busy prepping for our presentation.

Melody