%%Board of Directors (c)
\section{Board of Directors}
\subsection{Purpose}
The Board of Directors shall primarily 
discuss and make operational management decisions relating to the legal, 
financial, human resources, and high-level organizational strategy of the Society.

\subsection{Composition}
The Board of Directors is comprised of up to twelve (12) members:
\begin{itemize}
    \item The five (5) Executive, as defined in this document; 
  \item Two representatives from Council; and
  \item Five at-large representatives.
\end{itemize}

\noindent Additionally, the following shall serve as non-voting resource members:
\begin{itemize}
  \item The Speaker of Council;
  \item The Secretary of Council;
  \item The undergraduate student Senator(s) representing the Faculty; and
  \item The Dean of the Faculty, or designate.
\end{itemize}

If a person qualifies as both a voting and non-voting member of the Board of 
Directors, then they are a voting member.

In the event that one or more seats become vacant the
Board of Directors may appoint a social member or Councillor of the Society,
as the case may be, to fill the vacancy until such a time as a replacement may be duly elected.

\subsection{Terms of Office}
Members of the Board of Directors shall hold office for one (1) year, with the
exception of the Councillor representatives who will serve for one (1) term as
defined in this document. If a succesor is not found prior to the end a 
Councillor or Executive's term of office, that member will continue to serve 
until a replacement is found. 

Directors or Directors-elect can resign by written submission to the rest of
the Board of Directors. 

\subsection{Duties \& Powers}
The Board of Directors has full power over Society affairs except as such would 
conflict with this document or a decision made at a general meeting or by a 
referendum.

The Board of Directors of the Corporation shall manage the affairs of the 
Society and shall make or cause to be made for the Society, in its name, any 
kind of contract which the Society may lawfully enter into and, save as 
hereinafter provided, generally may exercise all such other powers and do all 
such other acts and things as the Society is authorized to exercise and do.

The Board of Directors shall determine the dates for the November, March, and July 
General Meetings of the Society.

The Board of Directors is responsible to review the finances of the Corporation, and approve 
its annual budgets. Directors oversee the Executive in the performance of their jobs.

\subsection{Convocation}
Meetings of the Board of Directors may be called by any of the following;
\begin{itemize}
  \item The Chair of the Board of Directors;
  \item The President;
  \item Any three voting members of the Board of Directors, upon petition in writing;
  \item The Dean or his designate.
\end{itemize}

A meeting of the Board of Directors must occur at least once a month.

\subsection{Notice}
Notice must be provided at least five (5) business days in advance of any meeting to every
member of the Board of Directors unless that member explicitly waives their right to
notice before the start of the meeting.

A full description of the intended motion, such as the text of a
proposed amendment or agreement, must be provided, but the motion may be
amended before or after it is moved as long as the changes remain within the
scope of the motion for which notice was given.

The Board of Directors may designate a mailing list or similar forum to be the official notice
forum of the Board of Directors; if this is done, then any notice sent to that forum is
considered to have been sent to every voting member of Council regardless of
whether or not it was received by that member.

\subsection{Eligibility Requirements}
In order to serve as a Director, a member must be a math student, other than a 
first-year student, and be 18 years of age or older.

If a Director or Director-elect fails to meet these requirements, then they
do not lose their seat automatically, but may be removed from their seat by a
majority vote of the Board of Directors.

No member shall occupy more than one voting seat on the Board of Directors in the 
same term simultaneously. 

\subsection{Quorum}
One half plus one (1) of all voting members of the Board of Directors shall constitute 
a quorum.

\subsection{Sessions}
For greater certainty, each meeting as called in accordance with this document,
plus its adjournments, constitute a single session of the Board of Directors.

\subsection{Duties of Directors}
Directors must, in addition to what is otherwise set out in the by-laws, the policies, 
and the procedures of the Society:
\begin{itemize}
    \item Familiarize themselves with the by-laws, policies, 
        procedures, and any active agreements of the Society;
    \item Attend all Board meetings;
    \item Actively participate in decisions and strategy development.
\end{itemize}

\subsection{Remuneration of Directors}
Directors shall not receive monetary remuneration, excluding discounts, for serving as such,
though they may receive such remuneration for serving as officers or employees or in other 
capacities.
