\section{Elections}
\begin{annotation}
    This section is fine to understand, but all sections relating to a specific
    position should be updated to be with those positions. As well, this 
    section is currently out of date with resolutions of past General Meetings.
    
    \textbf{Tristan Potter, Spring 2018}
\end{annotation}

All aspects of election procedure not defined explicitly in this document may be
set by a decision of the Society.

\subsection{General Election}
General elections shall be held in the fall term for each of the three terms 
of the subsequent year. In an election, a candidate does not need to run for 
each of the three terms for which the election is held. A single ballot shall 
be taken from each voter for all three terms in conjunction, and the results 
shall be evaluated separately for each term, but a candidate cannot win a term 
for which they are not running.

Elections shall be conducted using a preferential ballot system.

\subsection{By-elections}
In the event that one or more seats on Council or any of the executive
positions become vacant during the first two months of a term, or is left
vacant after an election, a by-election shall be held for those seats. If a
seat is vacant for a future term, then a by-election may be held before the
start of the vacant seat’s term. If no by-election is held by the start of that
term, one shall be held as soon as possible after the term begins.

%% TODO Move the folowing to the relevent sections
\subsection{Elected Executive \& Upper-Year Reps}
For the Executive Officers other than the Appointed Executives and the
Representatives other than First Year and Software Engineering Representatives,
general elections shall be held in the fall term for each of the three terms of
the subsequent year. In an election, a candidate does not need to run for each
of the three terms for which the election is held. A single ballot shall be
taken from each voter for all three terms in conjunction, and the results shall
be evaluated separately for each term, but a candidate cannot win a term for
which they are not running. Elections shall be conducted using a preferential
ballot system.

\subsection{Appointed Executives}
The following executives shall be appointed for each term by the Board
of Directors in the previous term:
\begin{enumerate} 
    \item the Vice-President, Finances;
    \item the Vice-President, Internal; and,
    \item the Vice-President, Operations.
\end{enumerate}

\subsection{Election to Multiple Positions}
If a member is elected to both an Executive and a Representative seat
simultaneously, then they take the Executive seat and the votes cast in the
Representative election are reevaluated with the member disqualified. If a
Representative is elected to an Executive seat, then they lose their
Representative seat.
