\section{Officers}
The Officers of the Society shall be elected by the Board of Directors at its 
first meeting each year to serve for that year or until their successor is elected. 

The Officers of the Society shall serve for one year, or until their successor
is duly appointed. 

An Officer may not be a chairperson or executive member of a club or other 
organization receiving or petitioning to receive funds from the Society. 
An Director may not sign a cheque addressed to an organization of which they 
are a member unless the specific expenditure is explicitly authorized by 
the Board of Directors.

In the event that an officer is 
\subsection{Chair}
The Chair of the Society must be a Director.

The Chair has the following duties:
\begin{itemize}
  \item Serve as the presiding officer of the Board of Directors;
  \item Interpret this and any other governing documents of the Society, subject
    to appeal to Council or a general meeting;
    \item Serve as a resource to the other Directors,
    especially the Directors who are not Executives;
  \item Arrange for and advertise meetings of the Board of Directors;
  \item Ensure that all Directors have access to the official notice
    forum, if any;
  \item Ensure that meetings of the Board of Directors are called regularly; and
  \item Act as a liason between the Board of Directors and Council.
\end{itemize}

In the event that there is no Chair, the Speaker of Council shall assume the duties and
responsibilities of the Chair of the Society. 

\subsubsection{Secretary}
The Secretary has the following duties:
\begin{itemize}
  \item Serve as the secretary of Council;
  \item Record attendance of Council meetings, including when a member is more
    than one half-hour late for a meeting and if they sent notice of their
    absence;
  \item Distribute minutes of each Council or general meeting in a timely manner
    after that meeting;
  \item Absent a decision to the contrary by the assembly, serve as the
    secretary of general meetings;
  \item Report to Council when a Councillor is failing to meet the requirements
    of office; and
  \item Maintain and update the official copies of this document and any other
    vital documents of the Society, including internal policies and external
    agreements.
\end{itemize}

In the event that there is no Secretary of the Society, the Vice President, Academic,
shall assume the duties and responsibilities of the Secretary of the Society.

\subsection{Treasurer}
The Treasurer of the Society shall be the Vice President, Finance. 

The Board of Directors may appoint, from time to time as required, another Director
to serve as the Treasure of the Society. 

\subsection{Chief Executive Officer}
The Chief Executive Officer of the Society shall be the President.

The Chief Executive Officer has the following duties:
\begin{itemize}
  \item Arrange for, advertise, and, absent a decision of the assembly to the
    contrary, chair general meetings;
  \item Oversee the Math C\&D and the C\&D Manager
  \item Verify the validity of petitions of the Society;
  \item Serve as an ex-officio member of all committees and boards of the
    Society, except for committees whose purpose is primarily to nominate or
    recommend persons for an award or office;
\end{itemize}
