\section{The Coffee \& Donut Shop}
\subsection{Management Board}
\subsubsection{Composition}
There shall be a C\&D Management Board. The membership of the Board shall
consist of:
\begin{itemize}
\item The President
\item The Vice-President, Finances
\item The Vice-President, Operations
\item One person appointed by the Dean
\item One person appointed by the Vice-President, Administration \& Finance of
the Federation
\item Six additional members elected by Council as described below
\item The manager of the C\&D
\end{itemize}
The members appointed by Council shall be elected to terms of three academice
terms or until their replacements are elected. The terms shall be staggered so
that two seats become vacant at the start of each academic term. Council shall
appoint to the newly-vacant seats at the first meeting of each term. The members
appointed by Council shall not work as employees in the C\&D.

The chair of the Board shall be elected by the Board in each academic term for
the following academic term from among those who are and will be members for both
terms in question, including by way of reappointment, re-election, election to a
different position, or the like.

The secretary of the Board shall be elected by the Board at the start of each
term.

Quorum for the Board shall be one fewer than a majority of its Executive members
and members appointed by Council. Only those members shall be counted for
determining whether or not a quorum is present.

\subsubsection{Duties \& Powers}
The C\&D Management Board is responsible to manage the C\&D, and generally has
the power necessary to do so, as well as to generally delegate that power to any
subcommittees or to members or employees of the Society, the Federation, or the
University. It has the power to set hiring policies in accordance with
University hiring process and direct the Human Resources Committee in regards to
employees of the C\&D.

The C\&D shall have a separate bank account from the Society's primary account,
and the Board's power to manage and spend funds shall be limited to that
account.

The Board shall meet at least once in each month in which there are at least
three weeks of classes, and shall report to Council at least once each term.

The Board's decisions shall not conflict with any decision of the Society, and
it must follow instructions given to it by the Society. Its decisions are
subject to amendment or rescindment by superior bodies.

\subsection{Manager}
The Society shall hire a manager for the C\&D.

The manager of the C\&D shall be responsible for management of the C\&D under
the supervision of the Board and shall generally have the power to manage its
affairs, subject to the authority of the Board and other bodies of the Society.

\subsection{Capital Expenditures}
The manager's authority to approve capital expenditures is limited to
a maximum of \$500. The manager and the VPO can together approve capital
expenditures up to \$2000. The Board can approve capital expenditures up to
\$5000. Larger amounts must be approved by Council.

\subsection{Signing Authority}
Signing authority on the C\&D bank account shall be held by the President,
the VPF, and the manager of the C\&D. Two endorsements shall be required for
each cheque; normally from the manager and the VPF.

Signing authority on all accounts with the University held by the C\&D shall
be held by the manager.
