\section{Boards, Directors, and Appointed Executive}
effective December 4, 2002; replaces March 31, 1998

\subsection{Executive Assistants}
The Executive may, from time to time as needed, appoint individuals to assist them in their Office.
The term of Office for executive assistants is up to the discretion of the Executive Officer in question, but it may not exceed the term of Office of that Officer.

\subsection{Directors}
All Directors must be Social members of the Society or hold an equivalent membership in another student society recognized by the Federation.
Directors will be appointed by the Executive Officer to whom they report, subject to ratification by Council.
Directors may be removed by the Executive Officer to whom they report, subject to ratification by Council.
In the event that no one is appointed as Director of a board, the Executive Officer to whom that Director would report shall discharge all necessary duties of the Director.
Directors shall have a term of Office of one term, but may be re-appointed if otherwise eligible.

The Director of each Board shall:
\begin{enumerate}
\item Convene meetings of the Board;
\item Be the sole representative of the Board on Council and be responsible for all correspondence on behalf of the Board;
\item Recommend and administer all budgets for the programs and activities of the Board;
\item Maintain the record binder for the Board;
\item Maintain at least one office hour per week;
\item Prepare a written report at the end of each term outlining the activities of the Board over the past term of the Board to be filed in the record binder for that directorship for future reference;
\item In the event of an Annual General Meeting of the Society, prepare and present a report of the activities of the Board over the last year; and
\item Prepare a report to be presented for each council meeting by either themselves or a delegate in regards to the status of the Board.
\end{enumerate}
