\section{External Funding Committee}
\subsection{Composition and Appointment}
The committee will consist of the President, Vice President Finances, and three
other members appointed by Council each term. The President will call the first
meeting each term, and the committee shall appoint a chair at that meeting.

\subsection{Duties}
The External Funding Committee is responsible to make recommendations to Council
on any external funding requests received by the Society, and to recommend
updates to this rule as they become necessary. The committee shall meet as often
as required to review all the funding requests. The committee must meet at least
once per term.

\subsection{Conflicts of Interest}
If a member of the External Funding Committee is an executive member of an
organization or club that is requesting funding, then that member shall be
excluded from the proceedings of the committee that are explicitly related to
them. In particular, they shall not have a vote, or a right to speak or to be
present when such matters are discussed. If two or more members of the committee
have a conflict of interest, the committee shall report the matter with no
recommendation.

\subsection{Criteria for Consideration of External Funding Request}
The committee shall develop a set of criteria for consideration of the external
funding requests and recommend amendments to this policy to codify them by the
end of the Fall 2012 term.

\subsection{Procedure}
An external funding request is a request from an organization other than:
\begin{enumerate}
  \item MathSoc
  \item Any math club
  \item MEF
  \item \textit{math}\textsf{NEWS}
  \item MGC
  \item WiMugrad
  \item The Faculty
  \item Math Orientation
\end{enumerate}

When an external funding request is received, the committee shall automatically
be referred a motion to approve the request, and shall report to Council on the
motion as soon as is reasonable. The initial wording of the motion shall reflect
the original request. In case of any disagreement on the matter, the committee
shall set the initial wording.

The committee can set the process by which external funding requests are to be
submitted to the committee.
