\section{Locker Distribution}
effective December 4, 2002; replaces March 23, 1999

Each social member of the Society may sign up to use one locker each term, subject to availability.
No person may sign up for more than one locker.
Each person signing up for a locker must complete a locker sign up sheet, including their name, phone number, and student identification number, and agree to the booking terms below:
\begin{enumerate}
\item The Society is not responsible for any items kept in lockers.
\item It is understood that at the beginning of the academic term all locks will be cut after appropriate notice (as defined below).
\item Lockers shall not be used to store items forbidden by law or University policy, including but not limited to: weapons, any flammable substances, explosive devices, or illegal substances. Lockers should also not be used to store food, drink or other perishable items.
\item All lockers may be signed out for the current academic term.
\item Within the first two weeks of term for any non-booked lockers with a lock, if a person signs up for a locker, but finds an unauthorized lock on that locker, the following steps will be taken:
\item A notice to remove the lock within the next two business days will be put on the locker door.
\item The number of the locker as well as the date on which the lock should be removed will be recorded.
\item If the lock is still in place on or after the posted date then the lock will be cut off by the Office Management Board.
\item A notice will be put on the locker stating that the contents may be reclaimed in the Society office.
\item Persons who are not social members of the Society may not sign up for a locker sooner than one week after social members have been allowed to sign up.
\item Clubs recognized by the Society may request to have a particular locker reserved for the use of the club at the beginning of every term. However, a representative of the club must sign for that locker on behalf of that club before the locker is used.
\end{enumerate}
