\documentclass[11pt]{mathsoc}
\usepackage{constitution}

\title{Actuarial Science Club Constitution}

\begin{document}
%%% TITLE PAGE
%\mathsoctitle

%%% TABLE OF CONTENTS
\setcounter{tocdepth}{4}
{\large \tableofcontents}

\newpage

\section{Name}
The full name of the Club shall be “The University of Waterloo Actuarial 
Science Club”; its short name shall be “ActSci”.

\section{Purpose}
The University of Waterloo Actuarial Science Club (herein the Club)  
aims to increase students’ awareness and knowledge of the current actuarial 
profession, as well as to enhance the interactions amongst actuarial science 
students within the Faculty of Mathematics.  

This Club will serve as an important source for students to learn more about 
the field of actuarial science.  

\section{Membership}
Membership in the Club shall cost \$5 Canadian Dollars. All members must
pay for the cost of membership.

There are two levels of membership: Full Member and Associate Member.  

\subsection{Full Member}
Any Social member of the Mathematics Society of the University of 
Waterloo can be a full member of the Club. 

A Full Member is entitled to all the rights and privledges granted 
to an Associate Member, as well as the privledge to:
\begin{enumerate}
    \item Hold an executive position, and
    \item Attend events.
\end{enumerate}

\subsection{Associate Member}
Any person who pays their membership fee and is not a full member is an 
associate member of the Club. 

An Associate member may attend events, but has none of the other rights
and privledges attributed to a Full Member of the Club.

\section{Executives}

\subsection{President}
The President shall:
\begin{enumerate}
    \item Represent the Club to the Mathematics Society and all external 
        organizations; 
    \item Oversee all the vice-presidents; and
    \item Have signing authority.
\end{enumerate}
    
The President must have two prior experiences with the Club, including one term 
as a Vice President.

\subsection{Vice President, Finance}
The Vice President, Finance, shall:
\begin{enumerate}
    \item Create and update the budget of the Club;
    \item Process reimbursements and expenses; and
    \item Have signing authority. 
\end{enumerate}

The Vice President, Finance, must have 1 prior experience with the Club.

\subsection{Vice President, Events}
The Vice President, Events, shall:
\begin{enumerate}
    \item Oversee the Event Coordinators and Mentorship Coordinators; 
    \item Ensure that all events run smoothly. 
\end{enumerate}

The following positions report to the Vice President, Events:
\begin{enumerate}
    \item Two (2) Mentorship Coordinators, and
    \item Three (3) Event Coordinators.
\end{enumerate}

The Vice President, Events, must have 1 prior experience with the Club.

\subsection{Vice President, Communication}
The Vice President, Communication shall:
\begin{enumerate}
    \item Oversee the Newsletter Editor and Publicity Directors; and
    \item Ensure that members are made aware of events through posters, 
        Facebook events, and email. 
\end{enumerate}

The following positions report to the Vice President, Communication:
\begin{enumerate}
    \item One (1) Newsletter Editor, and
    \item Two (2) Publicity Directors.
\end{enumerate}

The Vice President, Communication must have 1 prior experience with the Club.

\subsection{Vice President, Administration}
The Vice President, Administration shall:
\begin{enumerate}
    \item Oversee the Website Manager; 
    \item Ensure that the office is clean; 
    \item Manages the manuals, including seeking funding for new manuals; 
        and
    \item Investigating new initiatives to help students with professional 
        actuarial exams. 
\end{enumerate}

One (1) Website Manager shall report to the VP Administration.

The Vice President, Administration, must have one (1) prior experience with the Club.

\subsection{Event Coordinator} 

The Event Coordinators shall collectively plan, run, and coordinate all Club 
events. Event Coordinators must collaborate on mentorship events with 
the Mentorship Coordinators.

There shall be three (3) Event Coordinators.

\subsection{Mentorship Coordinator}
The Mentorship Coordinators shall collectively plan, run, and coordinate all 
Club mentorship events in collaboration with the Event Coordinators.

There shall be two (2) Mentorship Coordinators.

\subsection{Newsletter Editor}
The Newsletter Editor shall be responsible for assembling Club newsletters
and ensuring that all newsletters are published.

There shall be one (1) Newsletter Editor.

\subsection{Publicity Director} (2)\\
The Publicity Director is responsible for ensuring that members are notified 
of events and services offered by the Club. This includes creating posters, 
Facebook events, and emailing students. 

There shall be two (2) Publicity Directors.

\subsection{Website Manager} 
The Website Manager shall be in charge of managing the website and ensuring 
all Club computers are operational.

There shall be one (1) Website Manager.

\section{Executive Selection Committee}
The Executives of the Acturial Science Club shall be appointed by the 
Executive Selection Committee. The committee must advertise the election
during the first week of classes, and Executives must be appointed by the end
of the second week.

The Executive Selection Committee shall be comprised of the Presidents and Vice 
Presidents of the preceding four (4) terms. When chosen the committee membership
shall include the President and Vice Presidents of the current term

The Executive Selection Committee shall be chaired by the most senior member 
of the Club from the preceding two terms who is not an applicant for President.

The seniority of positions will be determined by the following order, where 
the most senior is at the top. The member who had the position most recently 
shall have higher seniority. 

\begin{enumerate}
    \item President
    \item Vice President, Finance
    \item Vice President, Events
    \item Vice President, Communication
    \item Vice President, Administration
\end{enumerate}

The chair of the Executive Selection Committe shall be henceforth known as the
Chief Returning Officer (CRO) and is responsible for the honourable and fair
appointment of the Club Executives. The Chief Returning Officer shall not have
a vote on the committee, except to break a tie. 

The Cheif Returning Officer is responsible for all administrative duties 
required, including but not limited to:
\begin{enumerate}
    \item Creating and distributing posters;
    \item Calling meetings of the committee;
    \item Managing resumes, cover letters, and related documentation;
    \item Arranging interviews with applicants as necessary;
    \item Informing the committee of updates as required; and
    \item Ensuring the executive selection procedures in this document are 
        followed.
\end{enumerate}

The Executive Selection Committee shall choose the President and Vice 
Presidents for the current term. The President and Vice Presidents for the 
current term will then join the committee to appoint the remaining positions.

\section{Meetings}
A Quorum for a meeting is twenty (20) members or fifty percent (50\%) of 
members, whichever is lower.

\section{Impeachment}
The President and Vice Presidents may be removed by a majority vote by 
secret ballet at a meeting of the Club's Full Membership.

To call a meeting to remove the President or a Vice-President, either:
\begin{enumerate}
    \item Twenty-five percent (25\%) of the members must petition the 
        Executive in writing; or
    \item Each of the other executives must sign a petition for removal. 
\end{enumerate}

Five (5) business days notice must be given to the Club membership of the
meeting. 

To call a meeting to remove an executive who is not a Vice President or 
President, the President and Vice-President of the Executive for removal must 
agree to call the meeting.

If an impeachment occurs, the most senior Executive must notify the other 
executives and the Membership immediately via e-mail. Seniority shall be 
determined by the same method used to determine the Chief Returning
Officer.

The remaining executives may fill the vacant position through a fair and 
honourable system at their discretion. Upon filling the vacant seat the 
Membership must be notified via e-mail.

\section{Ammendments}
Ammendments to this document may be made via a majority vote of Full Members 
through a referendum as defined by MathSoc, or at meeting called for this purpose.  

All ammendments must be in compliance with MathSoc's Policies and Bylaws.

\section{Relationships}

\subsection{Mathematics Society of the University of Waterloo}
The Club is a part of the Mathematics Society.

The Club will receive financial support, recognition, and legal 
support through the Federation of Students as defined by the Memorandum of 
Understanding between the Mathematics Society and the Federation of Students.

The Club shall attempt to maintain contact with the Actuarial Science 
Representatives of the Mathematics Society Council.

\subsection{University of Waterloo ASNA Delegates}
The Club will provide Facebook publicity for the University of Waterloo
Acturial Science National Association Delegates (the Delegates) through social media posts
at the Clubs discretion.

The Club will allow the the Delegates to use the Club Office for meetings at the discretion
of the Vice President, Administration.

\section{Keys}
Keys will be given to the President and Vice-Presidents as per MathSoc Policy.

\end{document}
